---
title: "Relationship Between Crime Rate and Gross Domastic Product in Taiwan"
author: "Christine Hsieh, May Huang, Yi-Fang Lo"
date: "7/22/2019"
output: html_document
---
# Data about Crimes committed in Taiwan
First import the data about crimes in Taiwan
[source]()
Chinese characters were removced to avoid encoding and compatibility issue

```{r warning=FALSE,message=FALSE} 
rm(list=ls())
library(readr)
library(tidyverse )
crimerate <- read_csv("https://raw.githubusercontent.com/Vladislav292/2019summer-datasciece/master/vands.csv")
head(crimerate)
library(dplyr)
```
Then import the data about Taiwan's GDP
[source]()
```{r warning=FALSE,message=FALSE}
GDP <- read_csv("https://raw.githubusercontent.com/Vladislav292/2019summer-datasciece/master/GDP.csv", )
head(GDP)
```

Merge the two sets of data by the parameter "Year"
```{r warning=FALSE,message=FALSE}
data_merged <-merge(crimerate, GDP,by="year")

head(data_merged)
```

```{r}
ggplot(data=data_merged)+ geom_line(mapping=aes(x=year,y=total1))+ geom_point(mapping = aes(x=year,y=total1))
```

 Secondly, let us draw a graph to visualize the relationship between GDP and year
 
```{r}
ggplot(data=data_merged,mapping=aes(x=year, y = GDP)) + geom_point() + geom_line()
```

It is not difficult to see that our crime rate fluctuated while the GDP grew relatively steadily with time.
To see if crime rate is associated with our economic performance, let us draw a graph to visulaize the Crime-GDP relationship.

```{r}
ggplot(data=data_merged,mapping=aes(x=GDP, y =total1 )) + geom_point() + geom_smooth()
```

The relation, quite disappointing since we expected that crime rate should have negative correlation with GDP. <br/>
However, the more we ponder on our hypothesis, it is not difficult to find that crimes take in lots of forms and we should find only a fraction of them which should be highly related to economic circumstance-larcency. <br/>
As a result, we made a graph to visulize the GDP-larceny relationship
```{r}
ggplot(data=data_merged, mapping = aes(x=GDP,y=larceny1)) +geom_point()+geom_smooth()
```
```{r}
ggplot(data=data_merged, mapping = aes(x=di,y=totaler)) +geom_point()+geom_smooth()
```

The result shocked us again. So,we turned to annother factor that we believed would affect crime rate- education degree.
Let's first import the data we need.
```{r}
edu <- read_csv("https://raw.githubusercontent.com/ChristineHsieh1231/mii/master/Educational%20Attainment.csv", 
     col_types = cols(X10 = col_number(), 
         X11 = col_number(), X12 = col_number(), 
         X13 = col_number(), X14 = col_number(), 
         X15 = col_number(), X16 = col_number(), 
         X17 = col_number(), X18 = col_number(), 
         X19 = col_number(), X2 = col_number(), 
         X20 = col_number(), X21 = col_number(), 
         X22 = col_number(), X23 = col_number(), 
         X24 = col_number(), X25 = col_number(), 
         X26 = col_number(), X27 = col_number(), 
         X28 = col_number(), X3 = col_number(), 
         X4 = col_number(), X5 = col_number(), 
         X6 = col_number(), X7 = col_number(), 
         X8 = col_number(), X9 = col_number()))
edu = filter(edu, Year<2017)
edu = filter(edu, Year>1996)
crimeb = filter(crimerate, year>1996)
crimeb = filter(crimeb, year<2017)
edu = edu %>%
  rename(
    year = Year,
    t = X2,
    m = X3,
    f = X4,
    t0 = X5,
    m0 = X6,
    f0 = X7,
    s = X8,
    ms = X9,
    fs = X10,
    t1 = X11,
    m1 = X12,
    f1 = X13,
    t2 = X14,
    m2 = X15,
    f2 = X16,
    t3 = X17, 
    m3 = X18,
    f3 = X19,
    t4 = X20,
    m4 = X21,
    f4 = X22,
    t5 = X23,
    m5 = X24,
    f5 = X25,
    t8 = X26,
    m8 = X27,
    f8 = X28
    
  )
    
   
```

```{r}
ggplot(data = edu)+
geom_line(mapping=aes(x=year,y=t,group=1))+geom_point(mapping = aes(x=year,y=t))
```



```{r}
edu0 = edu %>% select(year,t0,m0,f0) %>% 
    mutate(class = "illiterate") %>% rename(t=t0, m=m0,f=f0)
edu1 = edu %>% select(year,t1,m1,f1) %>%
    mutate(class = "primary")%>% rename(t=t1, m=m1,f=f1)
edu2 = edu %>% select(year,t2,m2,f2) %>%
    mutate(class = "junior")%>% rename(t=t2, m=m2,f=f2)
edu3 = edu %>% select(year,t3,m3,f3) %>%
    mutate(class = "senior")%>% rename(t=t3, m=m3,f=f3)
edu4 = edu %>% select(year,t4,m4,f4) %>%
    mutate(class = "undergrad")%>% rename(t=t4, m=m4,f=f4)
edu5 = edu %>% select(year,t5,m5,f5) %>%
    mutate(class = "grad")%>% rename(t=t5, m=m5,f=f5)
edus = edu %>% select(year,s,ms,fs) %>%
    mutate(class = "self")%>% rename(t=s, m=ms,f=fs)
edu8 = edu %>% select(year,t8,m8,f8) %>%
    mutate(class = "other")%>% rename(t=t8, m=m8,f=f8)
edue = rbind(edu0,edu1,edu2,edu3,edu4,edu5,edus,edu8)

head(edue)

```

```{r}
fig=ggplot(data = edue,aes(x = year, y = t ,color=class ,group = class)) +
  geom_line()+
  geom_point()
fig
```
```{r}

gender<-edue %>%
  select(year,t,m,f,class) %>% 
    mutate(fp = f / t, mp = m / t)


sex<-gender%>%
  group_by(fp,mp)

CLASS<- factor(gender$class, levels = c("illiterate","primary", "junior", "	senior", "undergrad", "grad","self","other" ), ordered = TRUE )

```




```{r}
ggplot(data = gender, aes(x=class, y=fp),group=sex) 
  +geom_boxplot()
```
